Qubit tests from classical codes

### 2023-02-17 quantum_codes_test.tex
comments, updates

\begin{definition}[$\eps$-local presentation]
Let $\code$ be an $[n,k,d]_q$ linear code and $M$ be an $r$-local tester for $\code$. An \emph{$\eps$-local presentation of $(\code,M)$} is a pair $(\mM,A)$ of a tracial von Neumann algebra $\mM$ and a collection of projective measurements $A = \{A^i_a\}_{a\in\F_q} \subseteq\mM$ for $i\in\{1,\ldots,n\}$ such that for any $S\subseteq\{1,\ldots,n\}$ of size $|S|\leq r$ there are $|S|$ pairwise commuting projective measurements $\{B^{S,i}_b\}_{b\in \F_q}$, for $i\in S$, such that 
\begin{itemize}
\item $\sum_{a\in \F^S} M(S,a) \, \prod_{i\in S} B^{S,i}_{a_i}= \Id$ \hnote{was $1_{M(S,a)=1}$ but can be simplified}
\item The two measurement families $\{A^i\}_{S, i\in S}$ \hnote{Don't quite understand the subscripting, since $A^i$ only depends on $i$} and $\{B^{S,i}\}_{S, i\in S}$ are $(\eps,\nu')$-close, where $\nu'((S,i))=\nu(S)1_{i\in S}\frac{1}{|S|}$.
\end{itemize} 
\hnote{question about the name: why ``presentation''? the object here is a pair $(\mM,A)$ which looks syntactically the same as a code representation... should it be ``representation''?}
\end{definition}

@@

\begin{proof}
We start with the second assertion. Suppose that $G_{\code,M}$ is $\delta'$-robust, for some function $\delta'$. Let $(\mM,A)$ be be an $r$-local $\eps$-presentation of $(\code,M)$ \hnote{nomenclature: should just be $\eps$-local presentation?}, and for each $S\subseteq\{1,\ldots,n\}$ such that $|S| \leq r$, $\{B^{S,i}\}_{i\in S}$ the commuting family of projective measurements promised by the definition. Then for every $S$ there is a projection $P^S \in \mM_\infty$ and an isometry $w^S\in P^S \mM_\infty I_\mM$ such that 
\[ \Es{S \sim \nu} \Es{i\in S} \sum_a \big\| A^i_a - (w^S)^* B^{S,i}_{a}w^S \big\|_2^2 \,\leq\,\eps\;.\]
\hnote{was: ``for some $(\eps_S)$ such that $\Es{S\sim \nu} \eps_S \leq \eps$.'', but this notation is never used again, so just directly added the expectation over $S$ above.}
 For any $a\in\field^S$ let $\tilde{P}^S_a = \prod_{i\in S} B^{S,i}_{a_i}$. Then $\{\tilde{P}^S_a\}_{a\in\F_q^S}$ is a projective measurement such that
\begin{align}
\Es{S\sim \nu} \Es{i\in S} \sum_{a\in \F_q^S} \tau\big(  (w^S)^* \tilde{P}^S_a w^S \, A^i_{a_i}\big) 
&= \Es{S\sim \nu} \Es{i\in S} \sum_{b\in \F_q}\tau\big(  (w^S)^* B^{S,i}_b w^S\, A^i_{b}\big)\notag \\
&= \Es{S\sim \nu} \Es{i\in S} \frac{1}{2}\Big(\tau\big((w^S)^*w^S\big) + \tau(1) - \sum_{b\in \F_q} \big\|  (w^S)^* B^{S,i}_b w^S - A^i_{b}\big\|_2^2\Big) \notag\\
&\geq \,\frac{1}{2}(1-\eps+1-\eps)\;.\label{eq:s-g-1}
\end{align}
Starting from the $\{\tilde{P}^S_a\}$, let $\{P^S_a\}$ be the family of projective measurements on $\mM$ that is promised by Lemma~\ref{lem:pull-back}. By a simple averaging argument,
\begin{equation}\label{eq:s-g-1b}
\Es{S\sim \nu}\sum_a \big\| P^S_a - (w^S)^* \tilde{P}^S_a (w^S)\big\|_2^2 \,=\, O(\eps)\;. 
\end{equation}
We can write
\begin{align}
\Big|\Es{S\sim \nu} \Es{i\in S} \sum_a \tau\big( P^S_a A^i_{a_i}\big)
&- \Es{S\sim \nu} \Es{i\in S} \sum_a \tau\big( (w^S)^* \tilde{P}^S_a (w^S)A^i_{a_i}\big)\Big|\notag\\
&= \Big| \Es{S\sim \nu} \Es{i\in S} \sum_a \tau\big(\big((w^S)^* \tilde{P}^S_a (w^S)-P^S_a\big)A^i_{a_i}\big)\Big|\notag\\
&\leq \Es{S\sim \nu} \Es{i\in S} \sum_a \tau\big(\big|(w^S)^* \tilde{P}^S_a (w^S)-P^S_a\big|\big)\notag\\
&= O(\sqrt{\eps})\;,\label{eq:s-g-2}
\end{align}
where the second line uses $\|A^i_a\|\leq 1$ and the last is by Lemma~\ref{lem:l1-l2} and~\eqref{eq:s-g-1b}.
Together with~\eqref{eq:s-g-1} and using the definition of $G_{\code,M}$, we have shown that
\begin{equation}
 \sum_{(S,i)} \mu(S,i) \sum_{a\in \field^s}\sum_{b\in\field} D(S,i,a,b) \tau\big(  P^S_a  A^i_{b}\big) \,\geq \,1-O(\sqrt{\eps})\;.\label{eq:s-g-4}
\end{equation}
In other words $\omega(G_{\code,M};\strategy)\geq 1-\eps'$ for $\strategy$ the strategy with measurements $\{A^i_b\}$ and $\{P^{S}_a\}$ and some $\eps'=O(\sqrt{\eps})$. Using the definition of robustness we deduce that $(\mM,A,P)$ is $(\delta'(\eps'),\nu)$-close to a perfect strategy $(\mN,C,Q)$ for $G$. Since $\nu$ is uniform on $\{1,\ldots,n\}$ we may specialize to the $A$ measurements; using the definition of closeness there exists a projection $P\in \mM_\infty$ such that $\{C^i\}_a \subseteq P\mM_\infty P$ and $\Es{i}\sum_a \|A^i_a-w^* C^i_a w \|_2^2 \leq 2\delta'$, and moreover $\{C^i_a\}$ satisfy that for any $S$ in the support of $\mu$, $\{C^i_a\}$ pairwise commute for $i\in S$. Using the assumption that $(\code,M)$ is Abelian, all the $\{C^i_a\}$ commute and form a representation of $\code$.

>>>>

\begin{definition}[$\eps$-local presentation]
Let $\code$ be an $[n,k,d]_q$ linear code and $M$ be an $r$-local tester for $\code$. An \emph{$\eps$-local presentation of $(\code,M)$} is a pair $(\mM,A)$ of a tracial von Neumann algebra $\mM$ and a collection of projective measurements $A = \{A^i_a\}_{a\in\F_q} \subseteq\mM$ for $i\in\{1,\ldots,n\}$ such that for any $S\subseteq\{1,\ldots,n\}$ of size $|S|\leq r$ there are $|S|$ pairwise commuting projective measurements $\{B^{S,i}\}_{i \in S }$ with $B^{S_i} = \{B^{S,i}_b\}_{b\in \F_q}$ \hnote{what algebra do the $B^{S,i}$ live in? $\mM$ or $\mM_\infty$?} such that 
\begin{itemize}
\item $\sum_{a\in \F^S} M(S,a) \, \prod_{i\in S} B^{S,i}_{a_i}= \Id$ \hnote{was $1_{M(S,a)=1}$ but can be simplified}
\item The two measurement families $\{A^i\}_{S, i\in S}$ \hnote{Don't quite understand the subscripting, since $A^i$ only depends on $i$} and $\{B^{S,i}\}_{S, i\in S}$ are $(\eps,\nu')$-close, where $\nu'((S,i))=\nu(S)1_{i\in S}\frac{1}{|S|}$.
\end{itemize} 
\hnote{question about the name: why ``presentation''? the object here is a pair $(\mM,A)$ which looks syntactically the same as a code representation... should it be ``representation''?}
\end{definition}

@@

\begin{proof}
We start with the second assertion. Suppose that $G_{\code,M}$ is $\delta'$-robust, for some function $\delta'$. Let $(\mM,A)$ be be an $r$-local $\eps$-presentation of $(\code,M)$ \hnote{nomenclature: should just be $\eps$-local presentation?}, and for each $S\subseteq\{1,\ldots,n\}$ such that $|S| \leq r$, $\{B^{S,i}\}_{i\in S}$ the commuting family of projective measurements promised by the definition. Then for every $S$ there is a projection $P^S \in \mM_\infty$ and an isometry $w^S\in P^S \mM_\infty I_\mM$ such that 
\[ \Es{S \sim \nu} \Es{i\in S} \sum_{a \in \F_q} \big\| A^i_a - (w^S)^* B^{S,i}_{a}w^S \big\|_2^2 \,\leq\,\eps\;.\]
\hnote{was: ``for some $(\eps_S)$ such that $\Es{S\sim \nu} \eps_S \leq \eps$.'', but this notation is never used again, so just directly added the expectation over $S$ above.}
 For any $a\in\F^S_q$ let $\tilde{P}^S_a = \prod_{i\in S} B^{S,i}_{a_i}$; \hnote{added:} since the measurements $\{B^{S,i}\}_i$ are pairwise commuting, the order of the product does not matter. Then $\{\tilde{P}^S_a\}_{a\in\F_q^S}$ is a projective measurement such that \hnote{I don't get what's happening in these next few lines... what happened to the product over $B^{S,i}_{a_i}$ in the first line?}
\begin{align}
\Es{S\sim \nu} \Es{i\in S} \sum_{a\in \F_q^S} \tau\big(  (w^S)^* \tilde{P}^S_a w^S \, A^i_{a_i}\big) 
&= \Es{S\sim \nu} \Es{i\in S} \sum_{b\in \F_q}\tau\big(  (w^S)^* B^{S,i}_b w^S\, A^i_{b}\big)\notag \\
&= \Es{S\sim \nu} \Es{i\in S} \frac{1}{2}\Big(\tau\big((w^S)^*w^S\big) + \tau(1) - \sum_{b\in \F_q} \big\|  (w^S)^* B^{S,i}_b w^S - A^i_{b}\big\|_2^2\Big) \notag\\
&\geq \,\frac{1}{2}(1-\eps+1-\eps)\;.\label{eq:s-g-1}
\end{align}
Starting from the $\{\tilde{P}^S_a\}$, let $\{P^S_a\}$ be the family of projective measurements on $\mM$ that is promised by Lemma~\ref{lem:pull-back}. By a simple averaging argument,
\begin{equation}\label{eq:s-g-1b}
\Es{S\sim \nu}\sum_a \big\| P^S_a - (w^S)^* \tilde{P}^S_a (w^S)\big\|_2^2 \,=\, O(\eps)\;. 
\end{equation}
We can write
\begin{align}
\Big|\Es{S\sim \nu} \Es{i\in S} \sum_a \tau\big( P^S_a A^i_{a_i}\big)
&- \Es{S\sim \nu} \Es{i\in S} \sum_a \tau\big( (w^S)^* \tilde{P}^S_a (w^S)A^i_{a_i}\big)\Big|\notag\\
&= \Big| \Es{S\sim \nu} \Es{i\in S} \sum_a \tau\big(\big((w^S)^* \tilde{P}^S_a (w^S)-P^S_a\big)A^i_{a_i}\big)\Big|\notag\\
&\leq \Es{S\sim \nu} \Es{i\in S} \sum_a \tau\big(\big|(w^S)^* \tilde{P}^S_a (w^S)-P^S_a\big|\big)\notag\\
&= O(\sqrt{\eps})\;,\label{eq:s-g-2}
\end{align}
where the second line uses $\|A^i_a\|\leq 1$ and the last is by Lemma~\ref{lem:l1-l2} and~\eqref{eq:s-g-1b}.
Together with~\eqref{eq:s-g-1} and using the definition of $G_{\code,M}$, we have shown that
\begin{equation}
 \sum_{(S,i)} \mu(S,i) \sum_{a\in \field^s}\sum_{b\in\field} D(S,i,a,b) \tau\big(  P^S_a  A^i_{b}\big) \,\geq \,1-O(\sqrt{\eps})\;.\label{eq:s-g-4}
\end{equation}
In other words $\omega(G_{\code,M};\strategy)\geq 1-\eps'$ for $\strategy$ the strategy with measurements $\{A^i_b\}$ and $\{P^{S}_a\}$ and some $\eps'=O(\sqrt{\eps})$. Using the definition of robustness we deduce that $(\mM,A,P)$ is $(\delta'(\eps'),\nu)$-close to a perfect strategy $(\mN,C,Q)$ for $G$. Since $\nu$ is uniform on $\{1,\ldots,n\}$ we may specialize to the $A$ measurements; using the definition of closeness there exists a projection $P\in \mM_\infty$ such that $\{C^i\}_a \subseteq P\mM_\infty P$ and $\Es{i}\sum_a \|A^i_a-w^* C^i_a w \|_2^2 \leq 2\delta'$, and moreover $\{C^i_a\}$ satisfy that for any $S$ in the support of $\mu$, $\{C^i_a\}$ pairwise commute for $i\in S$. Using the assumption that $(\code,M)$ is Abelian, all the $\{C^i_a\}$ commute and form a representation of $\code$.
